---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ptvalue

<!-- badges: start -->
<!-- badges: end -->

The goal of ptvalue is to provide a simple class for manipulating and printing measures related to precision teaching (celeration, bounce, etc.).

## Installation

You can install the development version of ptvalue like so:

``` r
remotes::install_github("agkamel/ptvalue")
```

## Create a ptvalue

We can create precision teaching values with `ptvalue()`:

```{r example}
library(ptvalue)
ptvalue(c(0.5, 1.4, 2))
```

For all original values that are greater or equal than $1$, a prefixed $\times$ symbol is added. For all original values that are greater than $0$ and smaller than $1$, these value are converted to a value greater than $1$ and a prefixed $\div$ symbol is added:

```{r}
ptvalue(c(5, 2, 1.25))
ptvalue(c(0.2, 0.5, 0.8))
```

While ptvalue are printed, the original values are always conserved:

```{r}
x <- ptvalue(c(0.5, 1.4, 2))
x
unclass(x)
```

## Multiplications and divisions

Because original values are always conserved under the hood, this allows us to multiply and divide ptvalues:

```{r}
ptvalue(1.4) * ptvalue(2)
ptvalue(2) * ptvalue(1.4)

ptvalue(0.5) / ptvalue(2)
ptvalue(2) / ptvalue(0.5)
```


