---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ptvalue

<!-- badges: start -->
<!-- badges: end -->

The goal of **ptvalue** is to provide a S3 class for printing and for small manipulation of Precision Teaching (PT) values (for instance, values of celeration, bounce) inside a vector or a dataframe. These values, are usually written on a Standard Celeration Chart (Calkin, 2005), can be used for further calculation and to print a nice table for report or paper.

## Installation

You can install the development version of **ptvalue** like so:

``` r
remotes::install_github("agkamel/ptvalue")
```

## Create a vector of PT values

You can create PT values with `ptvalue()`:

```{r example}
library(ptvalue)
ptvalue(c(0.5, 1.4, 2))
```

For all original values that are greater or equal than $1$, a prefixed $\times$ symbol is added. For all original values that are greater or equal than $0$ and smaller than $1$, these value are converted to a value greater than $1$ and a prefixed $\div$ symbol is added:

```{r}
ptvalue(c(5, 2, 1.25))
ptvalue(c(0.2, 0.5, 0.8))
```

Negative values always raises an error.

```{r, eval=FALSE}
ptvalue(-1) # Raise an error
```

PT values created with `ptvalue()` can be stored in objects:

```{r}
x <- ptvalue(c(0.5, 1.4, 2))
x
```

...and be inserted in dataframe as well:

```{r}
pt_df <- tibble::tibble(
  phase = 1:3,
  celeration = x)
pt_df
```


The type of a `ptvalue` vector is `double`. The original values are always conserved under the hood, it is only the printing that is different. These can always be converted back:

```{r}
unclass(x)
as.double(x)
```

## Arithmetics and comparisons

Because original values are always conserved, this allows us to multiply PT values:

```{r}
# Multiplication is commutative
ptvalue(x) * ptvalue(2)
ptvalue(2) * ptvalue(x)
```

... and divide PT values:

```{r}
# Division is not commutative
ptvalue(x) / ptvalue(2)
ptvalue(2) / ptvalue(x)
```

PT values can be used with comparison operators as well:

```{r}
x < ptvalue(1.8)
x == ptvalue(1.4)
```

## Invert sign

You can invert signs of PT values with `invert_sign()`:

```{r}
x
invert_sign(x)
```

## Report PT values

Because PT values can be stored in dataframes, it helps us to generate beautiful tables for journal articles or reports.

```{r, fig.cap="Celeration by phase."}
pt_df |> 
  knitr::kable(col.names = c("Phase", "Celeration"))
```


