---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ptvalue

<!-- badges: start -->
<!-- badges: end -->

The goal of **ptvalue** is to provide a S3 class for printing and for small manipulation of Precision Teaching (PT) values (ex., values of celeration, bounce) inside a vector or a dataframe. These values, are usually written on a Standard Celeration Chart (Calkin, 2005; Pennypacker et al., 2003), can be used for further calculations and to print a nice table for report or paper. Some basic helper functions directly related to the manipulation of PT values are also provided.

As this package is could be imported inside other packages (ex., **ptchart**), it will stay small and simple. The dependency from other packages will also be kept minimal.

## Installation

You can install **ptvalue** with the following code

``` r
install.packages("ptvalue")
```

or you can install the development version as follow:

``` r
remotes::install_github("agkamel/ptvalue")
```

## Create a vector of PT values

You can create PT values with `ptvalue()`:

```{r example}
library(ptvalue)
ptvalue(c(0.5, 1.4, 2))
```

For all original values that are greater or equal than $1$, a prefixed $\times$ symbol is added. For all original values that are greater than $0$ and smaller than $1$, these values are also converted to values greater than $1$, but a prefixed $\div$ symbol is added:

```{r}
ptvalue(c(5, 2, 1.25))
ptvalue(c(0.2, 0.5, 0.8))
```

Negative values always raises an error.

```{r, eval=FALSE}
ptvalue(-1) # Raises an error
```

PT values created with `ptvalue()` can be stored in objects:

```{r}
x <- ptvalue(c(0.5, 1.4, 2))
x
```

...and be inserted in dataframe as well:

```{r}
pt_df <- tibble::tibble(
  phase = 1:3,
  celeration = x)
pt_df
```


The type of a `ptvalue` vector is `double`. The original values are always conserved under the hood, it is only the printing that is different. These can always be converted back:

```{r}
unclass(x)
as.double(x)
```

Finaly, PT values can be created with `times()` or `div()`. In particular, the function `div()` is convenient for creating decaying PT values without having to find the decimal format before. These following three examples return the same PT values:

```{r}
ptvalue(c(0.5, 0.25, 0.125, 0.0625))
ptvalue(c(1/2, 1/4, 1/8, 1/16))
div(c(2, 4, 8, 16))
```


## Arithmetics and comparisons

Because original values are always conserved, this allows us to multiply PT values:

```{r}
# Multiplication is commutative
ptvalue(x) * ptvalue(2)
ptvalue(2) * ptvalue(x)
```

... and divide PT values:

```{r}
# Division is not commutative
ptvalue(x) / ptvalue(2)
ptvalue(2) / ptvalue(x)
```

PT values can be multipled by a numeric values...

```{r}
ptvalue(x) * 2
```

...or divided:

```{r}
# Division is not commutative
ptvalue(x) / 2
2 / ptvalue(x)
```

PT values can be used with comparison operators as well:

```{r}
x < ptvalue(1.8)
x == ptvalue(1.4)
```

## Basic helper functions

You can invert signs of PT values with `invert_sign()`:

```{r}
x
invert_sign(x)
```

You can convert values to absolute multiplicative values with `abs_sign()` (times or div):

```{r}
abs_sign(x)
abs_sign(x, sign = "div")
```

Alternatively, `as_times()` and `as_div()` are wrappers of `abs_sign()`:

```{r}
as_times(x)
as_div(x)
```

## Report PT values

Because PT values can be stored in dataframes, it helps us to generate beautiful tables for journal articles or for reports.

```{r, fig.cap="Celeration by phase."}
pt_df |> 
  knitr::kable(col.names = c("Phase", "Celeration"))
```


